Linear stability of magnetized massive protoplanetary disks

### 2014-02-12 paper/results.tex
tex update

\subsection{Influence of self-gravity on the MRI through the linear
  response}  
Our goal here is to examine whether or not self-gravity can amplify
the density perturbations caused by the MRI. We choose a massive 
isothermal disk with $Q=0.2$, which is still expected to be marginally
stable to gravitational instability \citep[][who find
a critical value of  $Q\simeq 0.2$]{mamat10}.   
The upper disk boundary is set to $Z_s=H$.

@@

\subsubsection{Resistive case}

>>>>

\subsection{Influence of self-gravity on the MRI through the linear
  response}  
Our goal here is to examine whether or not self-gravity can amplify
the density perturbations caused by the MRI. We choose a massive 
isothermal disk with $Q=0.2$ (corresponding to $Q_\mathrm{2D}=0.72$),
which is still expected to be marginally 
stable to gravitational instability \citep[][who find
a critical value of  $Q\simeq 0.2$]{mamat10}.   
The upper disk boundary is set to $Z_s=H$.

@@

\subsubsection{Resistive case}
We repeat the above calculation for resistive disks. We fix
$\beta=100$. Fig. \ref{gravity_energy_resis}

\begin{figure}
  \includegraphics[width=\linewidth]{figures/compare_energy_resis}
  \caption{Maximum gravitational potential energy perturbation
    associated with the MRI in a self-gravitating disk with $Q=0.2$,
    for a range of midplane Elsasser numbers.   
    \label{gravity_energy_resis}}
\end{figure}

\begin{figure}
  \includegraphics[width=\linewidth]{figures/result_resis_sg}
  \caption{Example of a linear resistive MRI mode with significant
    gravitational potential perturbation.  
    \label{mri_massive_resis}}
\end{figure}
